Manuscript Template for a Data Analysis Project

### 2023-03-18 code/analysis_code/Sex/2_sex.Rmd
more EDA and modeling

```{r}
library(here)
library(tidyverse)
library(spdep)
```
https://github.com/ubikuity/List-of-neighboring-states-for-each-US-state
List-of-neighboring-states-for-each-US-state
```{r}
sex_df <- readRDS(here("data/processed_data/sex_new.rds"))
us_nabs <- readRDS(here("data/processed_data/us_nabs.rds"))

@@

h_male <- matrix(0, nrow(male_df), nrow(male_df))
h_male[cbind(match(us_nabs$StateCode, male_df$`State Abbreviation`), match(us_nabs$NeighborStateCode, male_df$`State Abbreviation`))]<-1
nablist_male <- mat2listw(h_male)
```

@@

Since the data frame for female is missing observations (due to 0) for Vermont and New Hampshire, we need to remove these from the neighbor list.
```{r}
female_df <- sex_df %>%
  filter(!grepl("Alaska", State),
         !grepl("Hawaii", State),
         Sex == "Female")
us_nabs_f <- us_nabs %>%
  filter(!grepl("VT", StateCode),
         !grepl("NH", StateCode))

h_female <- matrix(0, nrow(female_df), nrow(female_df))
h_female[cbind(match(us_nabs_f$StateCode, female_df$`State Abbreviation`), match(us_nabs_f$NeighborStateCode, female_df$`State Abbreviation`))]<-1
nablist_female <- mat2listw(h_female)

>>>>

```{r message=FALSE, warning=FALSE}
library(here)
library(tidyverse)
library(spdep)
```
https://github.com/ubikuity/List-of-neighboring-states-for-each-US-state
List-of-neighboring-states-for-each-US-state
```{r}
sex_df <- readRDS(here("data/processed_data/sex_new.rds"))
us_nabs <- readRDS(here("data/processed_data/us_nabs.rds"))

@@

h_male <- matrix(0, nrow(male_df), nrow(male_df))
h_male[cbind(match(us_nabs$StateCode, male_df$`State Abbreviation`), match(us_nabs$NeighborStateCode, male_df$`State Abbreviation`))]<-1
nablist_male <- mat2listw(h_male, style = "W")
```

@@

Since the data frame for female is missing observations (due to 0) for Vermont and New Hampshire, we need to remove these from the neighbor list.
```{r}
female_df <- sex_df %>%
  filter(!grepl("Alaska", State),
         !grepl("Hawaii", State),
         Sex == "Female")
us_nabs_f <- us_nabs %>%
  filter(!grepl("VT", StateCode),
         !grepl("NH", StateCode),
         !grepl("VT", NeighborStateCode),
         !grepl("NH", NeighborStateCode))

h_female <- matrix(0, nrow(female_df), nrow(female_df))
h_female[cbind(match(us_nabs_f$StateCode, female_df$`State Abbreviation`), match(us_nabs_f$NeighborStateCode, female_df$`State Abbreviation`))]<-1
nablist_female <- mat2listw(h_female, style ="W")

### 2023-03-18 products/manuscript/MANU.qmd
more EDA and modeling

---
title: "Manuscript Template for a Data Analysis Project"
subtitle: "Exploring Factors influencing HIV-related Mortality Rates in the Georgia -- 2018 - 2020"
author: Hayley Hemme
date: "`r Sys.Date()`"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../dataanalysis_template_references.bib
csl: ../apa.csl
---

>>>>

---
title: "Manuscript Template for a Data Analysis Project"
subtitle: "Spatial Investigation and Exploration of Factors influencing HIV-related Mortality Rates in the United States"
author: Hayley Hemme
date: "`r Sys.Date()`"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../dataanalysis_template_references.bib
csl: ../apa.csl
---
